---
title: "data"
author: "John Chua"
date: "10/14/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(tidyverse)
library(readxl)
library(janitor)
library(tigris)
library(leaflet)
library(haven)
library(gganimate)
library(rstanarm)
library(gtsummary)
library(gt)
library(broom.mixed)



```

```{r}
data <- read_csv("raw_data/Community_Development_Public_Service_Program_Activities_by_Neighborhood.csv") %>%
  clean_names()

filtered_data <- data %>%
  filter(fiscal_year == "2018-19") 
write_rds(filtered_data, "App/data.rds")

```

```{r}
district_level <- read.csv("raw_data/Community_Development_Public_Service_Program_Activities_by_Supervisor_District.csv") %>%
  clean_names()

write_rds(district_level, "App/data_new.rds")
```

```{r}
calfresh_monthly <- read_xlsx("raw_data/calfresh_monthly.xlsx") %>%
  clean_names()

write_rds(calfresh_monthly, "App/shiny_data/calfresh_monthly.rds")

p <- calfresh_monthly %>%
  filter(county == "San Francisco") %>%
           ggplot(aes(x = date, y = unemployment_monthly)) +
           geom_line() +
  theme_bw() +
  geom_point() +
  transition_reveal(date, range = NULL)

animate(p, end_pause = 30)
```

```{r}
PRI_calfresh <- read_csv("raw_data/PRI_calfresh.csv", col_types = cols(County = col_character(),
  FIPS = col_character(),
  `County Center X` = col_double(),
  `County Center Y` = col_double(),
  Consortium = col_character(),
  `Calendar Year` = col_double(),
  `CalFresh Eligibles CY` = col_number(),
  `PRI Estimate Frequency` = col_character(),
  `5 Year Estimate` = col_character(),
  PRI = col_character())) %>%
  clean_names()

write_rds(PRI_calfresh, "App/shiny_data/PRI_calfresh.rds")

PRI_calfresh_ggplot <- PRI_calfresh %>%
  filter(county %in% c("San Francisco", "Statewide")) %>%
  ggplot(aes(y = pri, x = calendar_year, color = county)) +
  geom_point() +
  transition_reveal(calendar_year, range = NULL) +
  labs(title = "Calfresh Program Reach - San Francisco vs Statewide", x = "Year", y = "Program Reach Index (%)") + theme_bw()

animate(PRI_calfresh_ggplot, end_pause = 30)

PRI_calfresh_ggplot

```

```{r}
calfresh_overall <- read_csv("raw_data/calfresh_overall.csv", col_types = cols(County = col_character(),
  `Calendar Year` = col_double(),
  `Elderly CalFresh July` = col_number(),
  `Age 18 to 59 CalFresh July` = col_number(),
  `Children CalFresh July` = col_number(),
  `ESL CalFresh July CY` = col_character(),
  `Total Population CY` = col_number(),
  `Total Elderly 60Plus CY` = col_number(),
  `Total Children Under 18 CY` = col_number(),
  `Total ESL Over age 5 CY` = col_character(),
  `Total SSI Recipients CY` = col_number())) %>%
    select(County, `Calendar Year`, `Elderly CalFresh July`, `Age 18 to 59 CalFresh July`, `Children CalFresh July`, `ESL CalFresh July CY`, `Total Population CY`, `Total Elderly 60Plus CY`, `Total Children Under 18 CY`, `Total ESL Over age 5 CY`, `Total SSI Recipients CY`) %>%
  clean_names()



statewide_avg <- calfresh_overall %>%
  filter(county %in% c("Statewide")) %>%
  mutate(elderly_cal_fresh_july = elderly_cal_fresh_july/31) %>%
  mutate(age_18_to_59_cal_fresh_july = age_18_to_59_cal_fresh_july/31) %>%
  mutate(children_cal_fresh_july = children_cal_fresh_july/31) %>%
  mutate(total_population_cy = total_population_cy/31) %>%
  mutate(total_elderly_60plus_cy = total_elderly_60plus_cy/31) %>%
  mutate(total_children_under_18_cy = total_children_under_18_cy/31) %>%
  mutate(total_ssi_recipients_cy = total_ssi_recipients_cy/31)

calfresh_overall <- calfresh_overall %>%
  filter(county == "San Francisco")

  
calfresh_total <- rbind(statewide_avg, calfresh_overall) %>%
  select(-esl_cal_fresh_july_cy, -total_esl_over_age_5_cy) 

write_rds(calfresh_total, "App/shiny_data/calfresh_total.rds")

calfresh_total %>%
  ggplot(aes(y = elderly_cal_fresh_july, x = calendar_year, color = county)) +
  geom_line() +
  transition_reveal(calendar_year, range = NULL) +
  labs(title = "Variable - San Francisco vs Statewide", x = "Year", y = "Count") + 
  theme_bw()


#animate(PRI_calfresh_ggplot, end_pause = 30)



```



```{r}
opp_zones_new <- read_csv("raw_data/opportunity_zones_new.csv", col_types = cols(census_tract = col_double(),
  Value = col_double(),
  agency = col_character(),
  project_name = col_character(),
  description = col_character(),
  funding = col_character())) %>%
mutate(NAME = census_tract) 


write_rds(opp_zones_new, "App/shiny_data/opp_zones_new.rds")


food_banks <- read_xlsx("raw_data/FoodBanks.xlsx")
  write_rds(food_banks, "App/shiny_data/food_banks.rds")


tract_data <- tracts(state = "CA", county = "San Francisco", cb = TRUE) %>%
  mutate(NAME = as.numeric(NAME)) %>%
  geo_join(opp_zones_new, by = "NAME") 

tract_data$Value[is.na(tract_data$Value)] <- 20


bins <- c(0, 20, 40, 60, 80, 100)
pal <- colorBin("Reds", domain = tract_data$Value, bins = bins)

getColor <- function(food_banks) {
  sapply(food_banks$lat, function(lat) {
  if(lat == 37.73230) {
    "green"
  } else {
    "orange"
  } })
}

icons <- awesomeIcons(
  icon = 'ios-close',
  iconColor = 'black',
  library = 'ion',
  markerColor = getColor(food_banks)
)

tract_data %>%      
  sf::st_transform(4326) %>% 
    mutate(popup = str_c("Census Tract: ",  "<strong>", NAME, "</strong>",
                       "<br/>",
                       "Agency: ", "<strong>", agency, "</strong>",
                       "<br/>",
                       "Project Name: ", "<strong>", project_name, "</strong>",
                       "<br/>",
                       "Funding: ", "<strong>", funding, "</strong>") %>%
                        map(htmltools::HTML)) %>%
  leaflet() %>%
  addTiles() %>%
    addProviderTiles("CartoDB") %>% 
    addAwesomeMarkers(data = food_banks, ~as.numeric(long), ~as.numeric(lat), icon=icons, label=~as.character(name)) %>%
    setView(-122.409981, 37.773972, zoom = 12) %>% 
    addPolygons(label = ~popup, fillColor = ~pal(tract_data$Value), weight = 2,
  opacity = 1,
  color = "white",
  dashArray = "3",
  fillOpacity = 0.7) 





```


```{r}
income_new <- read_xlsx("raw_data/income.xlsx") %>%
  clean_names() %>%
  rename(NAME = tract_code) %>%
  mutate(tract_median_family_income = tract_median_family_income * 1000) 

income_data <- tracts(state = "CA", county = "San Francisco", cb = TRUE) %>%
  mutate(NAME = as.numeric(NAME)) %>%
  geo_join(income_new, by = "NAME") 


income_bins <- c(0, 40000, 80000, 120000, 160000, 200000, 240000, 280000, Inf)
income_pal <- colorBin("Greens", domain = income_data$tract_median_family_income, bins = income_bins)

getColor <- function(food_banks) {
  sapply(food_banks$lat, function(lat) {
  if(lat == 37.73230) {
    "green"
  } else {
    "orange"
  } })
}

icons <- awesomeIcons(
  icon = 'ios-close',
  iconColor = 'black',
  library = 'ion',
  markerColor = getColor(food_banks)
)


income_data %>%
 sf::st_transform(4326) %>% 
    mutate(popup = str_c("Census Tract: ",  "<strong>", NAME, "</strong>",
                       "<br/>",
                       "Median Household Income (2019) ", "<strong>", tract_median_family_income, "</strong>") %>%
           map(htmltools::HTML)) %>%
  leaflet() %>% 
  addTiles() %>%
      addProviderTiles("CartoDB") %>% 
    addAwesomeMarkers(data = food_banks, ~as.numeric(long), ~as.numeric(lat), icon=icons, label=~as.character(name)) %>%
    setView(-122.409981, 37.773972, zoom = 12) %>% 
    addPolygons(label = ~popup, fillColor = ~income_pal(income_data$tract_median_family_income), weight = 2,
  opacity = 1,
  color = "white",
  dashArray = "3",
  fillOpacity = 0.7) %>%
  addLegend(pal = income_pal, 
            values = income_data$tract_median_family_income, 
            position = "bottomright", 
            title = "Median household incomes")

```


```{r}
minority_bins <- c(0, 20, 40, 60, 80, 100)
minority_pal <- colorBin("Blues", domain = income_data$minority_population, bins = minority_bins)

getColor <- function(food_banks) {
  sapply(food_banks$lat, function(lat) {
  if(lat == 37.73230) {
    "green"
  } else {
    "orange"
  } })
}

icons <- awesomeIcons(
  icon = 'ios-close',
  iconColor = 'black',
  library = 'ion',
  markerColor = getColor(food_banks)
)

income_data %>%
 sf::st_transform(4326) %>% 
    mutate(popup = str_c("Census Tract: ",  "<strong>", NAME, "</strong>",
                       "<br/>",
                       "Percent Minority Population ", "<strong>", minority_population, "</strong>",
                       "<br/>",
                       "Total Minority Population ", "<strong>", tract_minority_percent, "</strong>") %>%
           map(htmltools::HTML)) %>%
  leaflet() %>% 
  addTiles() %>%
      addProviderTiles("CartoDB") %>% 
    addAwesomeMarkers(data = food_banks, ~as.numeric(long), ~as.numeric(lat), icon=icons, label=~as.character(name)) %>%
    setView(-122.409981, 37.773972, zoom = 12) %>% 
    addPolygons(label = ~popup, fillColor = ~minority_pal(income_data$minority_population), weight = 2,
  opacity = 1,
  color = "white",
  dashArray = "3",
  fillOpacity = 0.7) %>%
  addLegend(pal = minority_pal, 
            values = income_data$minority_population, 
            position = "bottomright", 
            title = "Percent Minority Population")

```


```{r}
cases <- read_csv("raw_data/COVID-19_Cases_and_Deaths_Summarized_by_Geography.csv", col_types = cols(area_type = col_character(), id = col_double(), count = col_integer(), rate = col_double(), deaths = col_integer(), acs_population = col_integer(), last_updated_at = col_character(), multipolygon = col_character()))
cases <- cases %>%
  filter(area_type == "Census Tract") %>%
  select(1:10) %>%
  mutate(tract = as.numeric(str_sub(id, 6, 10))) %>%
  mutate(NAME = tract/100) 

  write_rds(cases, "App/shiny_data/cases.rds")


cases_data <- tracts(state = "CA", county = "San Francisco", cb = TRUE) %>%
  mutate(NAME = as.numeric(NAME)) %>%
  geo_join(cases, by = "NAME") 


#pal <- colorNumeric(palette = "magma", domain = data$count)
other_bins <- c(0, 20, 40, 60, 80, 100, 200, 300, Inf)
pal <- colorBin("YlOrRd", domain = data$count, bins = other_bins)

getColor <- function(food_banks) {
  sapply(food_banks$lat, function(lat) {
  if(lat == 37.73230) {
    "green"
  } else {
    "orange"
  } })
}

icons <- awesomeIcons(
  icon = 'ios-close',
  iconColor = 'black',
  library = 'ion',
  markerColor = getColor(food_banks)
)

cases_data %>%
 sf::st_transform(4326) %>% 
    mutate(popup = str_c("Census Tract: ",  "<strong>", NAME, "</strong>",
                       "<br/>",
                       "COVID-19 Cases: ", "<strong>", count, "</strong>") %>%
           map(htmltools::HTML)) %>%
  leaflet() %>% 
  addTiles() %>%
      addProviderTiles("CartoDB") %>% 
    addAwesomeMarkers(data = food_banks, ~as.numeric(long), ~as.numeric(lat), icon=icons, label=~as.character(name)) %>%
    setView(-122.409981, 37.773972, zoom = 12) %>% 
    addPolygons(label = ~popup, fillColor = ~pal(data$count), weight = 2,
  opacity = 1,
  color = "white",
  dashArray = "3",
  fillOpacity = 0.7) %>%
  addLegend(pal = pal, 
            values = cases_data$count, 
            position = "bottomright", 
            title = "COVID Cases")

```

```{r}
new_mrfei <- read_csv("raw_data/2_16_mrfei_data_table.csv", col_types = cols(
  state = col_character(),
  fips = col_double(),
  mrfei = col_double()
)) 

newer_mrfei <- new_mrfei %>%
  filter(state == "CA") %>%
  mutate(tract = as.numeric(str_sub(fips, 5, 10))) %>%
  rename(TRACTCE = tract)
  
  write_rds(newer_mrfei, "App/shiny_data/newer_mrfei.rds")


merged_mrfei <- tracts(state = "CA", county = "San Francisco", cb = TRUE) %>%
  mutate(TRACTCE = as.numeric(TRACTCE)) %>%
  geo_join(newer_mrfei, by = "TRACTCE") 

mrfei_bins <- c(0, 5, 10, 15, 20, 25, 30, 40, 65)
mrfei_pal <- colorBin("Oranges", domain = merged_mrfei$mrfei, bins = mrfei_bins)

getColor <- function(food_banks) {
  sapply(food_banks$lat, function(lat) {
  if(lat == 37.73230) {
    "green"
  } else {
    "orange"
  } })
}

icons <- awesomeIcons(
  icon = 'ios-close',
  iconColor = 'black',
  library = 'ion',
  markerColor = getColor(food_banks)
)


mrfei_map <- merged_mrfei %>%
 sf::st_transform(4326) %>% 
    mutate(popup = str_c("Census Tract: ",  "<strong>", NAME, "</strong>",
                       "<br/>",
                       "Modified Retail Food Environment Index: ", "<strong>", mrfei, "</strong>") %>%
           map(htmltools::HTML)) %>%
  leaflet() %>% 
  addTiles() %>%
      addProviderTiles("CartoDB") %>% 
    addAwesomeMarkers(data = food_banks, ~as.numeric(long), ~as.numeric(lat), icon=icons, label=~as.character(name)) %>%
    setView(-122.409981, 37.773972, zoom = 12) %>% 
    addPolygons(label = ~popup, fillColor = ~mrfei_pal(merged_mrfei$mrfei), weight = 2,
  opacity = 1,
  color = "white",
  dashArray = "3",
  fillOpacity = 0.7) %>%
  addLegend(pal = mrfei_pal, 
            values = merged_mrfei$mrfei, 
            position = "bottomright", 
            title = "CDC MRFEI Index")



```



```{r}
yourData = read_dta("App/shiny_data/ADULT.dta")
write.csv(yourData, file = "yourStataFile.csv")

```


```{r}
CIH_data <- read_csv("yourStataFile.csv", col_types = cols(
  .default = col_double()
)) 

filtered_CIH <- CIH_data %>%
  filter(fslevcb %in% c("1", "2")) %>%
  select(fslevcb, ak22_p1, ahedc_p1, ae2, ak28, ins, numcig, srage_p1)

  write_rds(filtered_CIH, "App/shiny_data/filtered_CIH.rds")


set.seed(10)
CIH_mod <- stan_glm(data = filtered_CIH, 
         formula = fslevcb ~ ak22_p1 + ahedc_p1 + ae2 + ak28 + ins + numcig + srage_p1,
         refresh = 0)
CIH_mod

table_regression <- tbl_regression(CIH_mod, intercept = TRUE) %>%
  as_gt() %>%
     tab_header(title = md("*Regression of Demographic Characteristics on Food Insecurity Status among Individuals in California*"), 
              subtitle = "The Effect of Annual Income, Educational Attainment, Fruit Consumption, Perceptions of Safety, Insurance Status, Number of Cigarettes Smoked Monthly and Age on Food Security") %>%
    tab_source_note("Source: California Health Interview Survey (2019)")


```

The dataset is from the adult sample of the California Health Interview Survey, conducted in 2019. It contains 4744 observations, drawn from a universe of respondents whose poverty level is less than 200% of the federal poverty level. 

The variables that I am regressing are:
fslevcb - a measure of food security. A 1 indicates that the respondent is food secure, a 2 indicates that they are food insecure.
ak22_p1 - a measure of household total annual income before taxes. This is a 19-point scale from less than $10000 to over $18000, with each 1 point increase representing an increase in annual income of $10000.
ahedc_p1 - a measure of educational attainment. This is a 9 point scale, ranging from no formal education/grades 1-8 to a Ph.D to equivalent.
ae2 - a measure of the number of times the respondent consumed fruits in the past month. 
ak28 - a measure of how often the respondent feels safe in their neighborhood. This is a 4 point scale, ranging from "all of the time" to "none of the time."
ins - a measure of whether the respondent is insured. "1" is coded "Yes" and "2" is coded "No."
numcig - a measure of the number of cigarettes smoked by the respondent each day. This is a 6 point scale, ranging from "none" to "20 or more".
srage_p1 - a measure of self-reported age. 

This model is a predictive one that attempts to determine how any given variable might predict food insecurity in a given individual. We can interpret the following from the regression:
1) The "intercept" is the food security status when all the other variables are held at 0. It is 1.5, indicating the midpoint between food security and food insecurity.
2) Annual household income is correlated with food security status. For every increase in annual household income of $10,000, the individual is 2% less likely to be food insecure. 
3) Educational attainment is correlated with food security status. For every increase in educational attainment of 1 on the 9 point scale, the individual is 2% less likely to be food insecure. 
4) There is no correlation between the number of times a respondent consumed fruit in the past month with their food security status.
5) Perception of insecurity is negatively correlated with food security status. For every increase of 1 on the 4 point scale of self-reported perception of safety in the neighborhood (ie the respondent feels more insecure), the individual is 11% more likely to be food insecure.
6) Current insurance status is not correlated with food security status.
7) The number of cigarettes smoked per month is negatively correlated with food security status. For every increase of 1 in the 6 point scale (approximately 5 cigarettes), the individual is 4% more likely to be food insecure.
8) Self-reported age is not correlated with food security status.


